Network packet generation for Artificial Intelligence\\

### 2020-02-27 paper1/paper1.tex
Continued implementing feedback from Boris

\smallskip Worms: a software that spreads independently by exploiting vulnerabilities \cite{b6}. Examples include mass mailing worms, which spread via email, and network-aware worms, which only require four steps to infect a foreign host and spread themselves \cite{b2}.

@@

\medskip The classification model offers a comprehensive view of attacks. For example, for a worm that is distributed via email (dimension 1), the target Windows 95 (dimension 2) with an inadequate configuration (dimension 3) and a virus as payload (dimension 4) is determined. Further dimensions could be specified, for example what damage is caused by an attack, or how many costs arise from successfully carrying out the attack. Overall an overview is provided of how attacks can be classified, which attack targets are possible, or which vulnerabilities exist.

@@

There is a large number of network tools available in the world wide web. Many of them are free to download and can be used for malicious activities but there are also many that are for defensive purposes. Generally speaking there are two major groups: tools for network attackers and tools for network defenders.\cite{b1} The tools for network attackers are the ones generating the packets thus being the ones we will focus on.

@@

\smallskip Table \ref{table:sniffing-tools} contains a list of sniffing tools that are available online. Generally speaking sniffing tools do not generate packets and are therfore undetectable. However, on a switched ethernet network segment a sniffer does generate a small amount of packets such as ARP\cite{b9}. Other types of sniffers, such as Ettercap, can execute a Man-in-the-middle attack. This causes a lot of packets to be sent through the network as it needs to answer requests in order to spoof an identity.

>>>>

\smallskip Worms: a software that spreads independently by exploiting vulnerabilities \cite{b6}. Examples include mass mailing worms, which spread via email, and network-aware worms, which require only a few steps to infect a foreign host and spread themselves \cite{b2}.

@@

\medskip The classification model offers a comprehensive view of attacks. For example, for a worm that is distributed via email (dimension 1), the target Windows 95 (dimension 2) with an inadequate configuration (dimension 3) and a virus as payload (dimension 4) could be determined. Further dimensions could be specified, for example what damage is caused by an attack, or how many costs arise from successfully carrying out the attack. Overall an overview is provided of how attacks can be classified, which attack targets are possible, or which vulnerabilities exist.

@@

There is a large number of network tools available in the world wide web. Many of them are free to download and can be used for malicious activities but there are also many that can be used for defensive purposes. Generally speaking there are two major groups: tools for network attackers and tools for network defenders.\cite{b1} The tools for network attackers are the ones generating the packets thus being the ones we will focus on.

@@

\smallskip Table \ref{table:sniffing-tools} contains a list of sniffing tools that are available online. Generally speaking, sniffing tools do not generate packets and are therfore undetectable. However, on a switched ethernet network segment a sniffer does generate a small amount of packets such as ARP\cite{b9}. Other types of sniffers, such as Ettercap, can execute a Man-in-the-middle attack. This causes a lot of packets to be sent through the network as it needs to answer requests in order to spoof an identity.
